CES analysis for Paul Brockway rebound paper

### 2016-03-18 Articles/Brockway_Rebound_2015/Brockway_2015.Rnw
Now resamples UK 1980-->2010.

<<Resampling>>=
resampleFileName <- file.path("models", "Brockway2015Resamples.rds")
if (!rerunResamples){
  # load resample data from the file on disk
    resampleCoeffs <- readRDS(resampleFileName)
} else {
  # Run resampling on models.
  resampleCoeffs <- leaf_apply(l = models, class = c("cesModel", "plm"), f = function(mod, mod_name){
    resampledFits(mod, method = "wild", n = nResamples)$coeffs %>%
      mutate(
        Country = mod_name
      )
  }) %>% bind_rows
  saveRDS(resampleCoeffs, file = resampleFileName)
}
@

>>>>

<<Resampling>>=
resampleFileName <- file.path("models", "Brockway2015Resamples.rds")
resampleUK1980FileName <- file.path("models", "Brockway2015UK1980Resamples.rds")
if (!rerunResamples){
  # load resample data from the file on disk
    resampleCoeffs <- readRDS(resampleFileName)
    resampleCoeffsUK1980 <- readRDS(resampleUK1980FileName)
} else {
  # Run resampling on models.
  resampleCoeffs <- leaf_apply(l = models, class = c("cesModel", "plm"), f = function(mod, mod_name){
    resampledFits(mod, method = "wild", n = nResamples)$coeffs %>%
      mutate(
        Country = mod_name
      )
  }) %>% bind_rows
  saveRDS(resampleCoeffs, file = resampleFileName)

  # UK model for years 1980-2010
  resampleCoeffsUK1980 <- resampledFits(modelsUK1980$U, method = "wild", n = nResamples)$coeffs
  saveRDS(resampleCoeffsUK1980, file = resampleUK1980FileName)
}
@
